Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-06-07 paper/experiments.tex
Revision

The mean convergence plots of the tested algorithms on the benchmark functions
are given in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
regrets are listed in Table~\ref{tab:result_analytical}. As can be seen in
Figure~\ref{fig:CovPlotBenchmark} and Table~\ref{tab:result_analytical}, when
running in sequential mode, the MACE algorithm is competitive with the LCB and
EI acquisition functions. The sequential MACE (MACE-1) algorithm gave better
performances than the sequential EI (EI-1) and sequential LCB (LCB-1)
algorithms in the Eggholder, Branin, Hartmann6, Ackley10, and Rosenbrock10
functions. Also, the parallel MACE (MACE-4) gave the best performances among
all the tested algorithms for six out of the eight benchmark functions, and has
shown dramatic speedup compared to the sequential MACE. We also performed
additional experiments with varied batch sizes, the detail of those
experimental results can be seen in the supplementary materials.

>>>>

The mean convergence plots of the tested algorithms on the benchmark functions
are given in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
regrets are listed in Table~\ref{tab:result_analytical}. As can be seen in
Figure~\ref{fig:CovPlotBenchmark} and Table~\ref{tab:result_analytical}, when
running in sequential mode, the MACE algorithm is competitive with the LCB and
EI acquisition functions. The sequential MACE (MACE-1) algorithm gave better
performances than the sequential EI (EI-1) and sequential LCB (LCB-1)
algorithms in the Eggholder, Branin, Hartmann6, Ackley10, and Rosenbrock10
functions. Also, the parallel MACE (MACE-4) gave the best performances among
all the tested algorithms for six out of the eight benchmark functions, and has
shown dramatic speedup compared to the sequential MACE. We also performed
additional experiments with varied batch sizes, the detail of those
experimental results can be seen in the supplementary materials. We report the
time spent on the ten-dimensional Rosenbrock function optimization with $B = 4$ as a measure
of the algorithm overhead, for the ten-dimensional Rosenbrock function, it took
MACE about 11 hours to finish all the $N_{iter} = 175$ iterations, the BLCB algorithm took about
five hours, for the EI-LP algorithm, it took only one hour to finish the optimization. The overheads for qEI and qKG are much larger, it took
more than two days for qKG and qEI to finish the optimization of the ten-dimensional Rosenbrock function.
